% !TEX program = xelatex

\documentclass{resume}
\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Jeb Lee}

\basicInfo{
   Address: Henry St, Sheffield S3 7EQ, UK
  \email{jishen027@gmail.com} \textperiodcentered\ 
  \phone{07419127308 } \textperiodcentered\ }
  \linkedin {https://www.linkedin.com/in/jeblee} \textperiodcentered\
  \github {https://github.com/jishen027}

  \section{\faCogs\ Skills}
  \begin{itemize}[parsep=0.5ex]
    \item \textbf{Programming Languages:} JavaScript, Java, C\#, Python, PHP, YAML, Bash, HTML/CSS
    \item \textbf{Frameworks and Libraries:} React.js, Next.js, Vue.js, Laravel, Express.js, TailwindCSS
    \item \textbf{Database and Caching:} MongoDB, MySQL, Redis
    \item \textbf{Tools and Technologies:} Webpack, Websocket, Nginx
    \item \textbf{Cloud Services and DevOps:} Docker, Kubernetes, AWS (EKS, EC2, S3, RDS, Route 53, CloudFront, Lambda, CloudWatch), CI/CD
  \end{itemize}

\section{\faUsers\ Experience}
\datedsubsection{\textbf{Oasis Studio Group Ltd} Chesterfield, UK}{Sep. 2022 -- Present}
\role{Software Developer}{Full-time}
\begin{itemize}[noitemsep]
  \item Spearheaded the development of a comprehensive web analysis platform, utilizing \textbf{React.js}, \textbf{TailwindCSS}, and a suite of technologies. Integrated \textbf{OpenAI APIs} to enable advanced data analysis, resulting in a 30\% increase in efficiency for monthly report generation.
  \item Pioneered a dynamic CMS for Unity-based 3D virtual exhibitions, leveraging \textbf{Vue.js} and \textbf{Laravel}. The system, equipped with \textbf{WebSocket} for real-time updates, enhanced content management efficiency by 25\%.
  \item Developed an innovative multi-user server for 3D virtual exhibitions, optimizing performance through \textbf{Socket.io} and \textbf{Docker}. Achieved a 20\% improvement in load balancing and server responsiveness.
  \item Engineered a remote control service for VR headsets using \textbf{Socket.io}, \textbf{Express.js}, and \textbf{Vue.js}. This innovation enabled real-time, seamless administrator control of virtual content, enhancing user experience.
  \item Implemented and integrated \textbf{Stripe payment services} in multiple projects, streamlining bank card payments and subscription services, resulting in a 15\% increase in transaction efficiency.
  \item Transitioned to automated testing and deployment using \textbf{Docker}, \textbf{Azure DevOps}, and \textbf{Kubernetes}. Integrated ChatGPT for task management, increasing operational efficiency by 20\%.
\end{itemize}

\datedsubsection{\textbf{MyFair.co Ltd} Seoul, South Korea}{Jun 2019 -- Nov 2019}
\role{Junior Web Developer}{Internship}
\begin{itemize}
  \item Developed an intelligent business matching system using \textbf{Vue.js} and \textbf{SpringBoot}, \textbf{GraphQL}, \textbf{Mysql}. specifically tailored for Korean small businesses to expedite their international development opportunities.
  \item Implemented responsive website design updates using \textbf{CSS} and \textbf{JavaScript}, enhancing user experience and accessibility across various devices.
  \item Utilized data from an online expo booking platform to facilitate \textbf{smart business matchmaking}, fostering global connections.
  \item Integrated an expos map feature into the existing website, utilizing \textbf{JavaScript} and the \textbf{Google Map API} for improved navigational ease and user interaction.
\end{itemize}


\section{\faServer\ Recent Projects}

\subsection*{\textbf{Prompt Not Found - A website for sharing Prompts}}
\href{https://promptnotfound.com}{\textbf{Link}: https://promptnotfound.com}  \\
\textbf{Technologies Used:} AWS(EC2, S3, Route 53, GitHub Action, EKS, ECR), Next.js, Express.js, MongoDB, TailwindCSS.  \\
\textbf{Description:} Developed a website for sharing writing prompts, enabling users to create, share, and comment on prompts, fostering a community of writers.

\subsection*{\textbf{Virtual Public Consultation}}
\href{https://virtualconsultation.the360expo.com}{\textbf{Link}: https://virtualconsultation.the360expo.com}  \\
\textbf{Technologies Used:} Vue.js, Laravel(Sanctum, Fortify, Cashier), MySQL, Express.js, WebSocket, Stripe, Azure Pipeline(CI/CD) \\
\textbf{Description:} Engineered a 24/7 accessible online platform for community planning consultations, enhancing user engagement through an interactive interface and real-time features.

\subsection*{\textbf{Vantage Touchscreen}}
\href{https://www.vantage.eyesiteview.uk/frontend/testsite}{\textbf{Link}: https://www.vantage.eyesiteview.uk/frontend/testsite}  \\
\textbf{Technologies Used:} Vue.js, Laravel, MySQL, Socket.io, Google Maps \\
\textbf{Description:} Developed an interactive touchscreen system for sales centers, integrating CGI content like 360 tours and site plans, significantly improving customer experience and interaction.

\subsection*{\textbf{Predicting Player Action: A Novel Approach Using Polynomial Logistic Regression in FPS Games}}
\href{https://youtu.be/5FW23rIC7p0}{\textbf{Video Demo}: https://youtu.be/5FW23rIC7p0}  \\
\textbf{Technologies Used:} Python, Flask, Machine Learning, Jupyter Notebook, Javascript \\
\textbf{Description:} This project enhances FPS game controls using a Python-based backend with Flask and a JavaScript frontend. It employs machine learning to interpret player intentions from gamepad inputs, offering a more intuitive gaming experience through advanced technology integration. \\
% Education
\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{The University of Sheffield}, Sheffield, Uk}{2021 -- 2022}
\textit{M.S.} in Advanced Computer Science(CS), Sep. 2021 -- Sep. 2022.
\datedsubsection{\textbf{Ajou University}, Suwon, Korea}{2016 -- 2020}
\textit{B.S.} in Computer and Software Engineering(CSE), Sep. 2016 -- Aug. 2020.

\section{\faHeartO\ Honors and Awards}
\datedline{\textit{\nth{1} 2019-2 AJOU SOFTCON Research Division: Excellence Award}, Award on Ajou University }{Oct. 2019}

%% Certificate
\section{\faCertificate\ Certification}
\datedline{\textit{\href{https://www.freecodecamp.org/certification/JebLee/foundational-c-sharp-with-microsoft}{Foundational C\# with Microsoft}}}{Dec. 2023}

\section{\faInfo\ Miscellaneous}
\begin{itemize}[parsep=0.5ex]
  \item \href{https://github.com/jishen027}{\textbf{GitHub}: https://github.com/jishen027}
  %\item \href{https://www.jeblee.co.uk}{\textbf{Website}: https://www.jeblee.co.uk}
  \item \href{https://www.linkedin.com/in/jeblee}{\textbf{LinkedIn}: https://www.linkedin.com/in/jeblee} 
  \item \textbf{Languages:} English - Fluent, Mandarin - Native speaker, Korean - Fluent
\end{itemize}


%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}


\end{document}
